Adapting bootstrap to our problem

### 2024-07-10 adapt_boot.Rmd
Variance much better for adapted bootstrap

```{r}
res <- comparison(100, 500)
```

```{r}
# If it is positive, the second method is the best to estimate the total
sum(res[[1]])
# 10 e.g.
# 18
```

```{r}
# If it is positive, the second method is the best to minimize the variance
sum(res[[2]])
# 2 e.g.
# 12
```

@@

Adapting bootstrap to the problem seems relevant.

>>>>

```{r}
res <- comparison(1000, 800)
```

```{r}
# If it is positive, the second method is the best to estimate the total
sum(res[[1]])
# With ncomp = 100 and B = 500
# 10 e.g.
# 18

# With ncomp = 1000 and B = 800
# -4
```

```{r}
# If it is positive, the second method is the best to minimize the variance
sum(res[[2]])
# With ncomp = 100 and B = 500
# 2 e.g.
# 12

# With ncomp = 1000 and B = 800
# 56
```

@@

Adapting bootstrap to the problem seems relevant: it does not improve much the estimator but it reduces its variance.
